Main Analysis

### 2024-05-13 Manuscript Analysis/main_analysis.Rmd
small changes to main analysis rmd
demo information summary

---
title: "Main Analysis"
author: "Micah E. Hirsch"
date: "2024-04-15"
output: html_document
---

@@

The purpose of this document is to analyze and report findings related to M. Hirsch's dissertation project.

library(rio)
library(tidyverse)
library(mgcv)
library(itsadug)
library(irr)

phrase_acc <- rio::import("Cleaned Data/repetition_accuracy.csv")

@@

pupil_data <- rio::import("Cleaned Data/cleaned_pupil_data.csv")

pupil <- pupil_data |>
  left_join(phrase_acc, by = c("subject", "trial", "targetphrase")) |>
  dplyr::select(!c(rep_acc_rel, correct_words_rel, rel_response)) |>
  dplyr::mutate(speaker = ifelse(speaker == "Control", 0, 1),
                rep_acc = ifelse(rep_acc == "accurate", 0, 1),
                speaker = factor(speaker, levels = c(0, 1), labels = c("Control", "ALS")),
                rep_acc = factor(rep_acc, levels = c(0, 1), labels = c("accurate", "inaccurate")),
                code = as.factor(code))

pupil1 <- pupil |>
  dplyr::filter(rep_acc != "")

>>>>

---
title: "Main Analysis"
author: "Micah E. Hirsch"
date: "2024-05-13"
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: hide

---

@@

The purpose of this document is to analyze and report findings related to M. Hirsch's dissertation project. The data preparation and analysis was conducted using R Version 4.3.3.

```{r, echo = F, warning = F, messsage = F}

# Load in Needed Packages

library(rio)
library(tidyverse)
library(mgcv)
library(itsadug)
library(irr)
library(ggpubr) # installl.packages("ggpubr")
library(gt) # install.packages("gt")
library(gtsummary) # install.packages("gtsummary")
library(glmmTMB) # install.packages("glmmTMB")
library(performance) # install.packages("performance")
library(sjPlot) # install.packages("sjPlot")

# Listener Demographics

The table below shows the demographic information for the listeners in this study. A total of 39 listeners were recruited to participate in the study. However, 1 participant withdrew from the study (their data was already destroyed before exporting the listener demographic dataset) and 4 participants were dismissed due to difficulty during the calibration phase of the study. Therefore, there ended up being 34 total listeners in this study. The demographic table shows the demographic information for the 34 participants included in the study (complete) and the 4 who were not able to be tracked by the eye-tracking camera (incomplete).

All listeners reported being a fluent speaker of English. However, two participants noted that their native language was different than American English. Their reported native languages were Turkish and Spanish.

```{r, warning = F, message = F}

demo <- rio::import("Cleaned Data/cleaned_listener_demo.csv") |>
  dplyr::mutate(gender = factor(gender, levels = c("Man", "Woman", "Nonbinary", "Questioning", "Prefer not to answer")),
                ethnicity = factor(ethnicity, levels = c("Hispanic/Latino(a/e)", "Not Hispanic/Latino(a/e)", "Prefer not to answer")),
                race = factor(race, levels = c("white/Caucasian", "Black/African American", "Asian/Asian American",
                                               "Native Hawaiian or Other Pacific Islander", "Native American or Alaska Native",
                                               "Biracial or Multiracial", "Prefer not to answer", "Race not listed")),
                native_lang = factor(native_lang, c("American English", "Not American English")))

demo_table <- demo |>
  dplyr::select(age, gender, ethnicity, race, native_lang, pupil_complete) |>
  tbl_strata(
    strata = pupil_complete,
    ~.x |>
      tbl_summary(type = list(age ~ "continuous",
                          gender ~ "categorical",
                          ethnicity ~ "categorical",
                          race ~ "categorical",
                          native_lang ~ "categorical"),
                  statistic = list(all_continuous() ~ "{mean} ({sd}, {min}-{max})",
                               all_categorical() ~ "{n} ({p}%)"),
                  digits = list(everything() ~ c(2)),
                  label = list(age ~ "Age",
                           gender ~ "Gender",
                           ethnicity ~ "Ethnicity",
                           race ~ "Race",
                           native_lang ~ "Native Language"))
    ) |>
  as_gt()

demo_table

demo_table |>
  gt::gtsave("Tables/demographic_table.html")

@@
